An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-25 Revision/response.tex

To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in MetaReview R3.

We have revised the manuscript accordingly. (Please see page 7, Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, highlighted in blue in the revised manuscript.) Furthermore, it should be noted that, in the "Single-Attribute Building and Single-Attribute Query" subsection of Section 4.2.2 on page 8, due to space constraints, we have removed two previous datasets (Audio and GloVe), as Audio is relatively small-scale, and GloVe's scale is similar to SIFT1M while its LID is similar to GIST1M.

%%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{All experiments were conducted on the same server mentioned in Section 4.1.3.
			However, in practice, server providers may use other hardware settings (with other processors and RAM).
			Would the server setting affect the relative ordering of methods in experiments?
			For example, if Intel Xeon processor is used, would there be any change of the top 3 methods in Figures 4,5,7,8?
			Would the CPU cache size affect the top 3 methods in those figures?}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We have added relevant experiments conducted on different servers in Section 4.2.4 and 4.3.4. Please refer to the response MR.R4 for more details.
%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

### 2025-07-25 VLDB2026/main.tex
1
update 4.2.4 Large-scale Datasets

	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead. The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications. We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level. Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}

@@

	\textit{\textbf{Index size.}} 
	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size. Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
	%On low-dimensional datasets (Deep, YT-Audio), 
	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
	\textcolor{orange}{DSG is an improvement over SeRF. Compared to SeRF, DSG stores additional information for each edge in its index structure, resulting in a significant increase in index size on large-scale datasets.
	}

>>>>

	\textit{\textbf{\textcolor{blue}{Large-scale Datasets.}}} 
	\textcolor{violet}{As shown in the figure~\ref{fig:attribute big dataset}, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets. However, this also comes with significant memory overhead. The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance. Furthermore, we do not present the experimental results for StitchedVamana because its recall consistently remains at a very low level. This is due to its search starting point being set to 0 by default, when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point.}

@@

	\textit{\textbf{Index size.}} 
	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size. Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
	%On low-dimensional datasets (Deep, YT-Audio),

	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
	\textcolor{orange}{DSG is an improvement over SeRF. Compared to SeRF, DSG stores additional information for each edge in its index structure, resulting in a significant increase in index size on large-scale datasets.
	}
